Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-06 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: wording

For the filter methods, the percentage of features was added to the models as a hyperparameter.
For \ac{PCA}, the number of main components was tuned instead.
Random Forest hyperparameter \texttt{\(m_{try}\)} was modified into power transformed version \(p^{m_{try}}\) (ranging from 1 to $p$) to work on relative values of the respective datasets feature count.
Here \(p\) is the number of features of the dataset.
This was necessary to ensure that \texttt{\(m_{try}\)} was not chosen out of bounds during tuning with respect to the datasets feature count.
After the filtering, only a subset of features of the task is used for optimizing the models hyperparameters.
The size of this subset is always different since the number of features is also optimized.
Hence, the value of \texttt{\(m_{try}\)} needs to be created dynamically based on the datasets feature count.

>>>>

For the filter methods, the percentage of dataset's features was added to the models as a hyperparameter.
For \ac{PCA}, the number of principal components was tuned instead.
Random Forest hyperparameter \texttt{\(m_{try}\)} was modified into power transformed \(p^{m_{try}}\) (ranging from 1 to $p$) to work on relative values of the respective datasets feature count.
Here \(p\) is the number of features of the dataset.
This was necessary to ensure that \texttt{\(m_{try}\)} was not chosen out of bounds during tuning with respect to the datasets feature count.
After the filtering, only a subset of features of the task is used for optimizing the models hyperparameters.
The size of this subset is always different since the number of features is also optimized.
Hence, the value of \texttt{\(m_{try}\)} needs to be created dynamically based on the datasets feature count.
